### 2018-04-06 Bucketing/background.tex
Bucketing changes (mostly long lines)

We decided to focus on theory exploration in the Haskell programming language as it has mature, state-of-the-art implementations (\qspec{} \cite{QuickSpec} and \hspec{} \cite{claessen2013automating}). This is evident from the fact that the state-of-the-art equivalent for Isabelle/HOL, the \textsc{Hipster} \cite{Hipster} system, is actually implemented by translating to Haskell and invoking \hspec{}.

>>>>

We decided to focus on the Haskell programming language since it has direct
applications in industry, a large selection of library code for testing and
mature, state-of-the-art MTE tools including \qspec{}~\cite{QuickSpec},
\hspec{}~\cite{claessen2013automating} and
\textsc{Speculate}~\cite{braquehais2017speculate}. Our overall approach is
agnostic to the underlying system, so could also be applied to other targets
such as the Isabelle/HOL, which has the
\textsc{IsaCoSy}~\cite{johansson2009isacosy}, \textsc{IsaScheme}~\cite{omar} and
more recent \textsc{Hipster}~\cite{Hipster} MTE tools. However, since
\textsc{Hipster} works by translating to Haskell and invoking \hspec{}, it seems
that improving the Haskell tools will give the most benefit.
